Application-Level Regression Testing Framework using Jenkins

### 2017-04-02 manuscript/manuscript.tex
Access Control subsection.

In addition, we restrict connections to OTP using pwauth and session control. 
This is accomplished using the Apache module \texttt{mod_authnz_external} (FIXME: Add Reference) which is also in the configuration file \texttt{/etc/httpd/conf.d/ssl.conf} inside the \texttt{<VirtualHost>} directive:
\begin{lstlisting}
# -- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe 
/usr/local/bin/pwauth+session
<LocationMatch / > 
AuthType Basic
AuthBasicProvider external
AuthName "NCSA RSA OTP login" 
AuthExternal pwauth+session
require valid-user  
RequestHeader unset "X-Forwarded-User"
RequestHeader set "X-Forwarded-User" (REMOTE_USER)
</LocationMatch>
\end{lstlisting}

Pwauth is called by \texttt{/etc/htpd/conf.d/authnz_external.conf}: 
\begin{lstlisting}
LoadModule authnz_external_module \
modules/mod_authnz_external.so
DefineExternalAuth pwauth pipe /usr/bin/pwauth
DefineExternalAuth pwauth+sssion pipe \
/usr/local/bin/pwauth+session
\end{lstlisting}

OTP is specified in \texttt{/etc/pam.d/pwauth}:
\begin{lstlisting}
#%PAM-1.0
auth	   required	/lib64/security/pam_securid.so
account    include      password-auth
\end{lstlisting}

The session control was implemented with a custom python script available here:
\begin{lstlisting}
/usr/local/bin/pwauth+session: 
https://github.com/reubendb/BasicAuthOTPSession
/blob/master/BasicAuthOTPSession.py#L1
\end{lstlisting}

With this setup, all OTP requests to the HTTP over SSL protocol (i.e. \texttt{https}) on port 443 by default) are forwarded to the Jenkins server and Jenkins responses are forwarded back to the client (i.e. web browser).

@@

\section{Authentication and Authorization}
\label{sec:AuthenticationAuthorization}

%\subsection{Security Considerations}
%CUT THE NEXT TWO PARAGRAPHS AND DESCRIPTION OF CONFIG FILES OR REDUCE SINCE IT IS COVERED ABOVE --GALEN
%Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. 
%Blue Waters is an OTP only restricted access system. 
%Jenkins has the ability to execute user-level commands on our login nodes. 
%It also has some unfortunate default settings. 
%The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password. 
%Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance. 
% This required us initially to test the deployment with our TDS. 
%This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins. 
%In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space. 
% The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.

%\subsection{Configuration Choices}
%The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  Jenkins is configured to listen on port 8080 by default and we restricted it to localhost only. A reverse proxy was configured to run Jenkins behind Apache HTTP Server and SSL for access to the administrative console. With this reverse proxy, apache accepts requests on port 80 and 443 of bwjenkins.ncsa.illinois.edu and forwards them to the Jenkins web server at localhost which is now firewall protected. Most of this configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted.

%\begin{lstlisting}
%NOTE: Install mod_authnz_external Apache package

%(Jenkins sever configuration file snippets below)

%/etc/ssh/sshd_config:
%Match Host bwbh1.ncsa.illinois.edu,
%bwbh2.ncsa.illinois.edu
%HostbasedAuthentication yes

@@

%/etc/httpd/conf.d/ssl.conf:
% # -- The following sets ReverseProxy for Jenkins
%ProxyRequests       Off
%ProxyPreserveHost   On
%AllowEncodedSlashes On
%<Proxy *>
%Order deny,allow
%Allow from all
%</Proxy>
%ProxyPass       / http://localhost:8080/ nocanon
%ProxyPassReverse / http://localhost:8080/
%ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
%RequestHeader set X-Forwarded-Proto "https"
%RequestHeader set X-Forwarded-Port "443"

%\begin{lstlisting}
% # -- OTP for Jenkins SSL connection
%DefineExternalAuth pwauth+session pipe 
%/usr/local/bin/pwauth+session
%<LocationMatch / > 
%AuthType Basic
%AuthBasicProvider external
%AuthName "NCSA RSA OTP login" 
%AuthExternal pwauth+session
%require valid-user  
%RequestHeader unset "X-Forwarded-User"
%RequestHeader set "X-Forwarded-User" (REMOTE_USER)
%</LocationMatch>
 %
%
%/usr/local/bin/pwauth+session(OTP caching): 
%https://github.com/reubendb/BasicAuthOTPSession
%/blob/master/BasicAuthOTPSession.py#L1
%
 % 
%/etc/pam.d/pwauth (for OTP):
 %#%PAM-1.0
%auth  required  /lib64/security/pam_securid.so
%account  include  password-auth
%\end{lstlisting}
%/etc/sysconfig/jenkins (restrict to localhost):
%JENKINS_PORT="8080"
%JENKINS_LISTEN_ADDRESS=127.0.0.1
%\end{lstlisting}
\subsection{LDAP with Jenkins} 
%To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
At first this failed because our LDAP is using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

\subsection{Configure Global Security}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
\caption{ Configure Global Security }
\label{fig:Configure-Global-Security}
\end{figure}
We allow access by username and LDAP groups. The permissions can be scoped for individuals and groups. An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.

>>>>

With this setup, all requests to the HTTP over SSL protocol (i.e. \texttt{https}) on port 443 by default) are forwarded to the Jenkins server and Jenkins responses are forwarded back to the client (i.e. web browser).

@@

\subsection{Authenticating with One-Time Password}

Although Jenkins supplies its own authentication mechanism with its built-in user and password database, we feel that it is inadequate for securing our instance. 
The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password \footnote{This is perhaps another artifact of Jenkins setup intended to intranet environment.} 
We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID (FIXME: Add references https://www.rsa.com/en-us/products/rsa-securid-suite, https://en.wikipedia.org/wiki/RSA_SecurID) token for authentication. 
In this section we describe how we accomplished that.

Our use of Apache HTTP Server as front-end allow us to use ''Basic Authentication`` (FIXME: Add Reference). Via \texttt{mod_authnz_external} module, one can use any external mechanism or program to authenticate. 
One example of an authenticator is the ''pwauth`` authentication program. 
It is a simple program that returns a status code given a login (username) and password.

Combined with the Pluggable Authentication Module (PAM) --- a Unix authentication framework ---, we use ''pwauth`` to authenticate against our RSA SecurID OTP infrastructure. 
This is set up in the file \texttt{/etc/pam.d/pwauth}:
\begin{lstlisting}
#%PAM-1.0
auth	   required	/lib64/security/pam_securid.so
account    include      password-auth
\end{lstlisting}

Jenkins can use the user information given by Apache HTTP server if one selects ''HTTP Header by reverse proxy`` for its security realm. 
This means that all authentication is handled by Apache. 
Authenticating directly to \texttt{pwauth} against RSA SecurID OTP however presents an issue. 
It is often the case that a request needs to re-authenticate. 
The web browser normally handles this seamlessly by caching the user's credentials.
However, this does not work since, by definition, OTP credentials can only be used once. 
The solution is to use a back-end authenticator with some form of session management.

To accomplish this, we wrote a small python script called ''BasicAuthOTPSession`` [FIXME: Add Reference] as the authentication mechanism, wrapping the real authenticator (i.e. \texttt{pwauth} with PAM for RSA SecurID in our case). 
For the first time, it calls the real authenticator. 
Once an authentication succeed, a session is created and the next request with the same credentials from the same IP address are deemed successful without going through the real authenticator. 
The session expires in a predefined amount of time. 
A new request within that time renew the session. 
If there is no more request within that time, the session expires.
When this happens, one has to authenticate again with the real authenticator.

Figure {FIXME: CREATE FIGURE) illustrates the authentication mechanism we describe. 
Most of the configuration is defined in the file \texttt{/etc/httpd/conf.d/ssl.conf}, immediately following listing [FIXME: CITE LISTING] inside the same \texttt{<VirtualHost>} directive:

\begin{lstlisting}
#-- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe 
  /usr/local/bin/BasicAuthOTPSession.py

<LocationMatch / > 
  AuthType Basic
  AuthBasicProvider external
  AuthName "NCSA RSA OTP login" 
  AuthExternal pwauth+session
  require valid-user  
  RequestHeader unset "X-Forwarded-User"
  RequestHeader set "X-Forwarded-User" (REMOTE_USER)
</LocationMatch>

\end{lstlisting}
The \texttt{<LocationMatch / >} directive ensures that every request to the secure HTTP site is authenticated.

\subsection{Authorization and Access Control}
\label{subsec:authorization}

Jenkins default authorization allows logged in (authenticated) users to have full control. 
We wanted a more fine-grained access control to our instance and therefore selected the ''matrix-based security`` option (see Figure \ref{fig:jenkinsAuthorization}). Using this option we can limit what access individual users and groups have to our Jenkins instance. 
For example we restrict most users (other than admin users) from having the ''Job Delete`` permission to prevent one user or group from deleting each other's jobs.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
\caption{Jenkins fine-grained authorization.}
\label{fig:jenkinsAuthorization}
\end{figure}

We use the built-in LDAP plugin to query our LDAP server what group a user belongs to.
This greatly simplifies managing the authorization since it can be done based on groups rather than just individual users. 
The LDAP plugins gets the user information from the HTTP header passed by the reverse proxy set up. 
Figure \ref{fig:LDAP-Jenkins} shows the screenshot of our LDAP configuration within Jenkins interface.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{Using LDAP with Jenkins.}
\label{fig:LDAP-Jenkins}
\end{figure}

Since Jenkins allows one to enter arbitrarily command to be executed on login nodes, we want to further mitigate security risk via firewall rules. 
In our installation, we only allow IP address originating from our institution block to access the secure HTTP portion and authenticate to access Jenkins. 
At NCSA, the non secure, read-only, HTTP portion is accessible from anywhere. 
At NICS, this access is only allowed from the institution IP block only.

@@
